\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-04-06 revision3_2581/paper.tex
Minor adjustment to authors

\author{
	Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Researcher \And
	Eric Scott\\Tufts University \AND
	Andreas Scharm\"uller\\Universit\"at Koblenz-Landau \And
    Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Tam\'as Stirling, Eric Scott, Andreas Scharm\"uller, Ralf B. Sch\"afer}

@@

Though the data sources exhibit some overlap in the provided
information, each has been selected because it also provides unique
information and we encourage the interested reader to consult the
related source for details.  However, we provide a brief overview in
the Supporting Information.

>>>>

\author{
	Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Researcher \And
	Eric R. Scott\\Tufts University \AND
	Andreas Scharm\"uller\\Universit\"at Koblenz-Landau \And
    Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

\Plainauthor{Eduard Sz\"ocs, Tam\'as Stirling, Eric R. Scott, Andreas Scharm\"uller, Ralf B. Sch\"afer}

@@

Though the data sources exhibit some overlap in the provided
information, each has been selected because it also provides unique
information and we encourage the interested reader to consult the
related source for details.
